% Modern Resume Template
% Author: Created for Nadja Rhodes

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}

% Page dimensions
\geometry{letterpaper, margin=0.6in}

% Colors
\definecolor{primarycolor}{RGB}{0, 84, 132} % Deep blue
\definecolor{secondarycolor}{RGB}{70, 130, 180} % Steel blue
\definecolor{accentcolor}{RGB}{220, 220, 220} % Light gray

% Format section headings
\titleformat{\section}
  {\Large\bfseries\color{primarycolor}}
  {}{0em}
  {}
  [\titlerule]

\titlespacing{\section}{0pt}{8pt}{4pt}

% Contact info command
\newcommand{\contactinfo}[5]{
  \begin{center}
    {\huge\textbf{#1}}\\[0.1em]
    {\large\textit{#2}}\\[0.3em]
    \begin{tabular}{ccccc}
      \faEnvelope\, \href{mailto:#3}{#3} &
      \faGithub\, \href{https://github.com/#4}{#4} &
      \faLinkedin\, \href{https://linkedin.com/in/#5}{#5} &
      \faGlobe\, \href{https://#4.github.io}{#4.github.io}
    \end{tabular}
  \end{center}
}

% Custom command for experience entries
\newcommand{\experienceentry}[5]{
  \noindent\textbf{#1} \hfill \textbf{#2}\\
  \textit{#3} \hfill \textit{#4}\\[-8pt]
  #5
}

% Custom command for education entries
\newcommand{\educationentry}[4]{
  \noindent\textbf{#1} \hfill \textbf{#2}\\
  \textit{#3} \hfill \textit{#4}
}

% Set hyperlink colors
\hypersetup{
  colorlinks=true,
  linkcolor=accentcolor,
  filecolor=accentcolor,
  urlcolor=secondarycolor,
}

% Tighter itemize environment
\setlist[itemize]{leftmargin=*, nosep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=1pt}

\begin{document}

% Header
\contactinfo{Nadja Rhodes}{Software \{Machine Learning\} Engineer}{narhodes1+res@gmail.com}{iconix}{nadjarhodes}

% Experience
\section{Work Experience}
\experienceentry{ASAPP}{Jan 2019 - Jul 2024}{New York, NY}{}{
\begin{itemize}
  \item \textbf{Staff Machine Learning Engineer} (Nov 2021 - Jul 2024)
  \begin{itemize}
    \item Led ML engineering team of 3, with collaboration from a \~{}dozen research scientists and product engineers, to productionize new LLM-based customer support agent for a Fortune 100 airline client, enabling automation complex call center interactions.
    \item Led team of 4 developing company-wide ML training framework used by all (\~{}20) models, standardizing pipelines, remote compute access, dataset and model management, and external tool integration.
    \item Architected multi-node distributed training on colocated servers using Kubernetes and Ray.io; collaborated on implementing training dataset indexing service for 10x faster dataset access (minutes to seconds).
    \item Proactively built internal Slack bot as passion project, providing thread summarization, ownership info, and trend detection to improve team communications.
  \end{itemize}
  \item \textbf{Lead Machine Learning Engineer} (Jan 2019 - Nov 2021)
  \begin{itemize}
    \item Architected centralized routing layer between applications and ML services, migrating critical NLU components while orchestrating parallel model calls and unifying responses with entity handling and intent classification.
    \item Led end-to-end development of named entity recognition service and entity highlighting for 1st voice client; owned domain-specific entity highlighting from planning to rollout, delivering 11\% increase in entity card hover rates.
  \end{itemize}
\end{itemize}
}

\vspace{0.3em}

\experienceentry{Microsoft}{Sep 2013 - Sep 2018}{Redmond, WA}{}{
\begin{itemize}
  \item \textbf{Software Engineer II} (Apr 2016 - Sep 2018)
  \begin{itemize}
    \item Rebuilt and open-sourced \href{https://github.com/OneNoteDev/WebClipper}{OneNote Web Clipper} on modern, React-like framework; led JS testing infrastructure and client-side telemetry implementation.
    \item Led technical development of Web Clipper ratings prompt, increasing Chrome Web Store rating from 2.73 to 4.44 stars.
    \item Spearheaded GDPR compliance plan for exporting OneNote content; pioneered and patented ML efforts in incubation team of 3, developing task detection prototype.
  \end{itemize}
  \item \textbf{Software Engineer} (Sep 2013 - Apr 2016)
  \begin{itemize}
    \item Led development and public launch of \href{https://www.onenote.com/notebooks}{OneNote.com/notebooks} entry point (4M MAU, 58K daily visits), including first public endpoint for new storage layer.
    \item Enhanced backend for OneNote welcome emails and produced data-driven insights on site experimentation.
  \end{itemize}
\end{itemize}
}

% Education
\section{Education \& Scholarship}
\experienceentry{Deep Learning Scholar}{Summer 2018}{OpenAI}{San Francisco, CA}{
\begin{itemize}
  \item Granted \href{https://blog.openai.com/openai-scholars/}{scholarship} to study deep learning under \href{https://natashajaques.ai/}{Dr. Natasha Jaques}; focused on language modeling and generative text for NLP.
  \item Developed and open-sourced deephypebot, a generative language model that creates music commentary on Twitter. (\href{https://github.com/iconix/deephypebot}{Code}, \href{https://youtu.be/-6Aq5Q0c-CU}{Talk})
\end{itemize}
}

\vspace{0.3em}

\educationentry{B.S. Computer Science}{2009 - 2013}{Stanford University, School of Engineering}{Stanford, CA}

% Career Development Section
\section{Career Transitions \& Industry Engagement}
\begin{itemize}
  \item \textbf{Recurse Center} (Nov 2024 - Feb 2025): Self-directed \href{https://www.recurse.com/}{programming retreat} in a peer-learning environment. Focused on web development, creative coding, and generative AI.
  \item \textbf{Family Sabbatical} (Jul - Nov 2024): Dedicated time for parenting and early childhood development.
  \item \textbf{Internships}: \href{https://www.rd.ntt/e/cs/}{NTT Communication Science Labs} (2012), Google BOLD (2011), Stanford Research (2010).
  \item \textbf{Presentations}: OpenAI Scholars Demo Day (2018, \href{https://youtu.be/-6Aq5Q0c-CU}{deephypebot}); \textbf{Conferences}: RenderATL (2023), ACL (2019), NSBE (2018), GHC (2016), Y Combinator FFC (2014).
\end{itemize}

\end{document}
